\section{Mission Overview}
The root requirement of a satellite-based ADS-B system is the provision of ADS-B coverage over regions where terrestrial systems do not currently provide coverage (in particular, oceans and poles). Within this requirement are a number of variable mission parameters that effect the design and economic cost of resulting satellite systems. Varying the parameters and analysing the performance of resulting designs will allow for more effective mission trade-off analysis.

\subsection{System Users}
A spaced based ADS-B system would have two key user groups
\begin{itemize}
	\item Air Navigation Service Providers
	\item Airlines and air transportation service providers
\end{itemize}
Although Australia, America and Europe are able to implement terrestrial ADS-B stations, rolling out terrestrial stations to cover all interest areas is not necessarily cost effective. This is particularly true in regions such as South East Asia. In such regions, the technology and economic base does not exist to make terrestrial deployment viable \cite{Blomenhofer2012}. In these situations a satellite-based system can more effectively augment existing ADS-B coverage for use by ANSPs.

Another key user would be airlines and other air transportation services. Greater position and telemetry coverage of aircraft over oceanic and polar regions allows for more optimal flight path co-ordination. ADS-B assisted flight routing will allow for narrower longitudinal and latitudinal track separation, allowing for more flights to travel on desired fuel-saving paths. A flight simulation analysis presented by Iridium LLC suggests that increased density of planes in jet streams can result in fuel savings of up to 450 litres per oceanic flight \cite{Dawson2013}. 


\subsection{System Update Rate}
The update rate of a space-based ADS-B system defines timeliness with which aircraft data can be updated and disseminated terrestrially. Having a high-effective update rate is crucial in range of Airports with ATC towers having to co-ordinate a large density of aircraft traffic. With ADS-B, terrestrial ATC towers typically achieve an update rate of less than 1 second depending on airport capacity \cite{Orlando2001}. For the purposes of live tracking and safety control, an update rate in the order of 1 second to 30 seconds will be required. An update rate in the order of 5 to 10 minutes would enable satisfactory tracking by airlines and air transport services at less cost. A lowest cost system with an update rate of 1-2 hours could be useful for occasional tracking of aircraft making oceanic flights. This, however, would be inadequate for safety applications or any short-range terrestrial flights. 

\subsection{Revisit Time}
Due to the random access nature of Mode S Extended Squitter, the number of aircraft surveyed by an ADS-B receiver is limited. Scanning for a shorter period, or scanning an area with more aircraft will result in more ADS-B collisions and a drastically reduced detect rate. `Missing' aircraft in this manner is unacceptable from a safety perspective. Suggested solutions for high density areas include more sophisticated antenna design with spot beams \cite{Blomenhofer2012}, or variable-periodicity of ADS-B signals \cite{Orlando2001}. 

For ADS-B reception via satellite, a populated area can be either scanned for a longer period, or `re-scanned' over multiple revisits. This would mediate the need for a larger or more sophisticated and costly antenna array. A longer scanning period can be achieved slowing the ground-track of the space segment over key areas. This is particularly a problem on CubeSats where technology implementation is limited. The revisit time will therefore be defined by limitations of the antennae array and on-board processing technology for ADS-B signal reception. Satellite ADS-B receivers are currently being tested by the German Aerospace Centre (DLR) in conjunction with the European Space Agency (ESA) \cite{DLR} and Thales Alenia Space \cite{Blomenhofer2012}.

\subsection{Geographical Coverage}
Full global coverage would be achieved by a series of polar or near polar orbits, such as the Iridium Satellite constellation \cite{iridium_ICAO_man,iridium:an_overview1998}. Achieving full coverage would be the most costly solution, requiring the largest number of satellites and ground stations. At the very least, the ADS-B system should cover the poles, the North Atlantic, North Pacific and Indian Oceans and South East Asia in order to meet the root system requirement. These areas have the highest amount of air traffic not covered by terrestrial ADS-B systems as shown in Figure \ref{fig:flightpaths}.  Monitoring these regions with specific orbits can reduce the number of spacecraft required in order to provide the coverage gap required by the system.

